---
title: "Exploratory Data Analysis- Markdown Homework"
author: "Tina Vo"
date: "3/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This project has two raw data files at different scales from a study of infants, children, and adults watching a series of 7 video clips. I wrote Steps 1 and 2 to import and merge the data, and kept them there for your reference. Skip down to Step 3 to work on EDA

### SOURCE DESCRIPTION

## FILE 1: auc.csv

Columns:

  * stim (stimulus video, levels/labels provided below)
  * id (unique participant identifier)
  * age (in days)
  * AUC_sal (area-under-the-curve for a saliency model)
  * AUC_dist (area-under-the-curve for a distance model)

AUC values indicate how well each model predicted where participants looked when watching a video.AUC values can range from 0-1 where .5 is chance and 1 is perfect prediction

## FILE 2: participants_info_full_headers.csv

Columns:

  * id (unique participant identifier, matches auc.csv)
  * age_group (a categorical age variable with levels:
  * ".5-1 y" "1-1.5 y" "1.5-2 y" "2-4 y" "4-6 y" "8-10 y" "adult"   * precision (a quality measure of the eye data, smaller is better)
  * 7 columns of "Seen X" the stimulus video before the study coded as SEEN (1), NOT SEEN (2), NOT SURE (3) 


### STEP 1: Read in AUC data

Code stim as a factor
```{r, echo=FALSE}
auc <- read_csv(here("data_raw", "auc_bystim.csv"))
stim_levels <- 1:7
stim_labels <- c("Fallon","Feist","Pentatonix","Science","Rube","Plane","Dogs")
auc <- auc %>% mutate(stim = factor(stim, levels = stim_levels, labels = stim_labels))

```


